Software Citation Principles

### 2016-05-09 sc-principles/software-citation-principles.tex
Reword 5.4 software peer review
The wording of this section made it sound like citation was completely
irrelevant to the peer review process. I don't think it is entirely so,
therefore I replaced the first sentence and reworded the rest
accordingly

This document does not discuss peer review of software, which is an important issue but is
also mostly out of scope in the context of software citation principles.
Since the goal of software citation is to identify the software
that has been used in a scholarly product, whether or not that software has been peer-reviewed
is irrelevant.  One possible exception would be if the peer-review status of the software should
be part of the metadata, but the working group does not believe this to be part of the
minimal metadata needed to identify the software.

>>>>

Adherence to the software citation principles enables better peer reviews through improved reproducibility. However, since the primary goal of software citation is to identify the software that has been used in a scholarly product, the peer review of software is mostly out of scope in the context of software citation principles. For instance, when identifying a particular software artifact that has been used in a scholarly product, whether or not that software has been peer-reviewed is irrelevant. One possible exception would be if the peer-review status of the software should
be part of the metadata, but the working group does not believe this to be part of the
minimal metadata needed to identify the software.
